Music Recommendation System Using the Million Song Dataset

### 2015-05-07 writeup/MSDgroupwriteup.tex
Update MSDgroupwriteup.tex

One explanation for the very low MAP scores using PMF was that the number of plays that were used are different from what PMF is typically used for which is bounded ratings. Using implicit user feedback (number of plays) instead of explicit user feedback (ratings) have been found in literature to create various issues. One of the main issues is that implicit feedback is inherently noisy and does not measure negative feedback. Users may have played a song to simply find out that they dislike the song. The other main issue is that the exact number of plays could have a significantly different meaning across different users. For example, an avid user who has played a song five times could have a different meaning to a user that has at most only played songs five times.

>>>>

One explanation for the very low MAP scores using PMF was that the number of plays that were used are different from what PMF is typically used for which is bounded ratings. Using implicit user feedback (number of plays) instead of explicit user feedback (ratings) has been found in literature to create various issues. One of the main issues is that implicit feedback is inherently noisy and does not measure negative feedback. Users may have played a song to simply find out that they dislike the song. The other main issue is that the exact number of plays could have a significantly different meaning across different users. For example, an avid user who has played a song five times could have a different meaning as compared to a user that has at most only played songs five times.
